WIDS 2024 Final Presentation

### 2024-01-12 Documents/Presentation.qmd
update t test values

@@

::: columns
::: {.column width="60%"}
-   Our regression analysis shows that the south and north central regions in the United States are the main regions that have seen union membership rates and political leanings show increased correlation.
-   T-test between union and non union wages
    -   1980s: t = 22.846, df = 9.4096, p-value = 1.462e-09
        -   mean of x = 26.306; mean of y = 20.375
        -   95% CI: (5.347, 6.514)
    -   2010s: t = 22.846, df = 9.4096, p-value = 1.462e-09
        -   mean of x = 30.533; mean of y = 25.664
        -   95% CI: (3.786, 5.952)
:::

@@

"Johnthegeek". 2021. “Wealth and income over time.” GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-02-09/readme.md.

"Johnthegeek". 2023. “Union Membership in the United States.” GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-09-05/readme.md.

"Johnthegeek". 2023. “US House Election Results.” GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-11-07/readme.md.

"LisleJoem". 2021. “US Minimum Wage by State from 1968 to 2020 and 2020 Equivalent Dollars.” Kaggle. https://www.kaggle.com/datasets/lislejoem/us-minimum-wage-by-state-from-1968-to-2017.

>>>>

-   The decline of organized labor in the United States coincided with a large increase in wage inequality. From 1973 to 2007, men's wage inequality increased by 40 percent, from .25 to .35, with most of the rise unfolding from 1978 to 2000.

-   ..even in a period of labor weakness (2000-2014), union activism increases the wages of union members.

-   "Particularly since the early 2000s, when the Bush administration's NLRB appointments led to a series of decisions that were especially hostile to organized labor ([Liebman 2007](https://muse.jhu.edu/article/659928#b25); [Farber 2014](https://muse.jhu.edu/article/659928#b15)).

@@

::: columns
::: {.column width="60%"}
-   Our regression analysis shows that the south and north central regions in the United States are the main regions that have seen union membership rates and political leanings show increased correlation.
-   T-test between union and non union wages
    -   1980s: t = 22.846, df = 9.4096, p-value = 1.462e-09
        -   mean of x = 26.306; mean of y = 20.375
        -   95% CI: (5.347, 6.514)
    -   2010s: t = 9.5488, df = 15.629, p-value = 6.393e-08
        -   mean of x = 30.533; mean of y = 25.664
        -   95% CI: (3.786, 5.952)
:::

@@

"Johnthegeek". 2021. "Wealth and income over time." GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-02-09/readme.md.

"Johnthegeek". 2023. "Union Membership in the United States." GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-09-05/readme.md.

"Johnthegeek". 2023. "US House Election Results." GitHub. https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-11-07/readme.md.

"LisleJoem". 2021. "US Minimum Wage by State from 1968 to 2020 and 2020 Equivalent Dollars." Kaggle. https://www.kaggle.com/datasets/lislejoem/us-minimum-wage-by-state-from-1968-to-2017.

## Bibliography pt 2 {.smaller}

Western, B., & Rosenfeld, J. (2011). Unions, norms, and the rise in U.S. wage inequality. American Sociological Review, 76(4), 513-537.\
Retrieved from <https://www.proquest.com/scholarly-journals/unions-norms-rise-u-s-wage-inequality/docview/908813088/se-2>

Wilmers, Nathan. "Labor Unions as Activist Organizations: A Union Power Approach to Estimating Union Wage Effects." Social Forces, vol. 95, no. 4, 2017, pp. 1451--77. JSTOR, <http://www.jstor.org/stable/26166881> Accessed 9 Jan. 2024.

Freeman, Richard. et al. How Does Declining Unionism Affect the American Middle Class and Intergenerational Mobility? / Richard Freeman, Eunice Han, David Madland, Brendan V. Duke. Cambridge, Mass: National Bureau of Economic Research, 2015. Print.
